\bf On semidefinite-representable sets over valuation fields

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{graphicx}
\usepackage{color}
\usepackage{ulem}
\usepackage{bm}

@@

The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
linear group in $R^{n \times n}$ is $\GL_n(R)$.
For the sake of ease of writing, block-diagonal matrices with blocks
$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null square
matrix of size $t$ by ${\bf 0}_{t}$, and the identity matrix by $I_t$.

We recall the definition of Smith Normal Form, in our context.
\begin{definition}[Smith Normal Form]\label{smith_nf}
  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  \mathrm{SNF}(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r}).
  $$
  The matrix $\mathrm{SNF}(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
  \emph{invariant factors}.
\end{definition}
\begin{remark}
  The valuation of the first invariant factor of $\mathrm{SNF}(M)$ of a matrix
  $M \in K^{n \times n}$ is the minimum of the valuations of the entries of
  $M$. In particular, $\mathrm{SNF}(M) \in \OK^{n \times n}$.
\end{remark}

@@

The optimization problem of miminizing a linear function over a real spectrahedron is called \emph{semidefinite programming} (SDP). Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
\begin{equation}
  \label{SDP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
\end{array}
\end{equation}
Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that $A(x) =
\ell_1(x) \oplus \cdots \oplus \ell_d(x)$. In other words, SDP is a generalization of Linear Programming (LP).

@@

A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé ``and
$D=0$'', car cela ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
we often refer to \eqref{LP} as a \emph{diagonal} linear program.
We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.

@@

\begin{algorithm}
    \caption{\textbf{SOLVELP}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
      \STATE find $x_0$ such that $Dx_0=e$
      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c,0,0)$
      \ENDIF
      \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
      \IF{$S \neq A$}
      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,0,0)$
      \RETURN $[\mathrm{STATUS}, P^{-1}y]$
      \ELSE
      \STATE
      \ENDIF
    \end{algorithmic}
\end{algorithm}

@@

We first prove a reduction result, allowing to consider only iterations
of~\eqref{LP} with data of the form $(A,b,c,0,0)$.

\begin{lemma}\label{reducD}
  Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
  $e \in K^m$ and let $J \in K^{n \times R}$ be a matrix such that
  ${\rm Im}\, J = \ker D$ and $R = \dim \ker D$.
  Assume there exists $x_0 \in K^n$ such that $D x_0 = e$, and let
  $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
  Let $y \in K^R$ denote the unique element of $K^n$ such that
  $x = x_0 + J y$. Then:
  \begin{enumerate}
  \item\label{reducD_item1}
    $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
  \item\label{reducD_item2}
    $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and
    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$\footnote{\simone{Est-ce que
    c'est bien $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$ ou plutôt la condition
    plus faible $\val \langle c,x^* \rangle = \val \langle J^T c,y^* \rangle$ ?
  Même question pour \Cref{solsLP}.}}.
  \end{enumerate}
\end{lemma}
\begin{proof}
  %The existence and uniqueness of $y$ are granted by the fact that $x \in x_0 + \ker D =x_0+ {\rm Im } J$  and $\ker J = \{0\}$. 
  First, if $D={\bf 0}$, then by the assumptions one must have $e=0$, and the problem
  is already reduced (with $J=I_n$ and $x_0=0$).
  Next, assume $D\neq{\bf 0}$, then $Dx=e$ and $Ax + b \le 0$ if and only if
  $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}. Finally, for all
  $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
\end{proof}

@@

\begin{lemma} \label{solsLP}
  Let $A \in K^{d\times n}$, $b \in K^d$, $c\in K^n$ and let
  $S = \mathrm{SNF}(A) = QAP^{-1} \in K^{d\times n}$, with
  $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$.
  Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
  Then
   \begin{enumerate}
   \item \label{solsLP_item1}
     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y = P x \in K^n$ is
     feasible for \eqref{LP} with data $(S,b',c',0,0)$.
   \item \label{solsLP_item2}
     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y^* = P x^*$ is
     a solution to \eqref{LP} with data $(S,b',c',0,0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
   \end{enumerate}
\end{lemma}
\begin{proof}
  Note that the transition matrices $P$ and $Q$ defining SNF$(A)$ are invertible in $\OK$
  and as such they preserve inequalities: $Mz \geq 0$ if and only if $Nz \geq 0$, with
  $N = \mathrm{SNF}(M)$. Thus one has that $Ax+b = AP^{-1}y +b \geq 0$ if and only if
  $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
  Moreover, for all $c \in K^n$, we have $\langle c, x\rangle = \langle c, P^{-1}Px \rangle =
  \langle (P^{-1})^T c, Px \rangle = \langle c',y\rangle$, which proves
  \Cref{solsLP_item2}.
\end{proof}

@@

\begin{lemma}\label{prop:reduc}
  Let $(A,b,c), (S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
  Then:
  \begin{enumerate}
  \item \label{prop:reduc_it1}
    \eqref{LP} with data $(S,b',c',0,0)$ is feasible if and only if the $d-r$ last coefficients
    of $b'$ have nonnegative valuation, for $r = {\rm rank}\,S$.
  \item \label{prop:reduc_it2}
    Assume at least one of the $n-r$ last coefficients of $c'$ is non-zero. If \eqref{LP} with
    data $(S,b',c')$ is feasible, then it is unbounded and does not admit solutions.
  \end{enumerate}
\end{lemma}
\begin{proof}
  %%%%\corentin{préciser les notations}. 
  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
  $(S,b',c',0)$ if and only if $\val(s_i y_i + b_i) \geq 0$ for\footnote{\simone{Ce n'est pas plutôt $\val(s_i y_i + b'_i) \geq 0$ ? Car c'est $b'$ et non pas $b$.}} all $i = 1,\ldots,n$.
  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
  necessarily the $d-r$ last coefficients of $b'$ have nonnegative valuation.
  Conversely, if the $d-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
  $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
  with data $(S,b',c',0,0)$.

  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',0,0)$.
  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',0,0)$,
  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
  In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$. Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}. 
\end{proof}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{graphicx}
\usepackage{color,xcolor}
\usepackage{ulem}
\usepackage{bm}

@@

The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
linear group in $R^{n \times n}$ is $\GL_n(R)$.
For the sake of ease of writing, block-diagonal matrices with blocks
$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null matrix of
size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix by $I_t$.

We recall the definition of Smith Normal Form, in our context.
\begin{definition}[Smith Normal Form]\label{smith_nf}
  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  \mathrm{SNF}(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{m-r,n-r}).
  $$
  The matrix $\mathrm{SNF}(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
  \emph{invariant factors}.
\end{definition}
\begin{remark}
  The valuation of the first invariant factor of $\mathrm{SNF}(M)$ of a matrix
  $M \in K^{n \times n}$ is the minimum of the valuations of the entries of
  $M$. In particular, $\mathrm{SNF}(M) \in \OK^{n \times n}$.
\end{remark}

@@

The optimization problem of miminizing a linear function over a real spectrahedron is called \emph{semidefinite programming} (SDP). Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
\begin{equation}
  \label{SDP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
\end{array}
\end{equation}
Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that
$A = \diag(\ell_1,\ldots, \ell_d)$. In other words, SDP is a generalization of Linear Programming (LP).

@@

A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé ``and
$D=0$'', car cela ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
we refer to \eqref{LP} as a \emph{diagonal} linear program.
We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.

@@

\begin{algorithm}
    \caption{\textbf{SOLVELP}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
      \STATE find $x_0$ such that $Dx_0=e$
      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
      \ENDIF
      \IF{$A$ not in Smith Normal Form}
      \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
      \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}}
      \ELSE
      \STATE
      \STATE
      \RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
      \ENDIF
    \end{algorithmic}
\end{algorithm}

@@

We first prove a reduction result, allowing to consider only iterations
of~\eqref{LP} with data of the form $(A,b,c,{\bf 0},0)$.

\begin{lemma}\label{reducD}
  Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
  $e \in K^m$ and let $J \in K^{n \times R}$ be a matrix such that
  ${\rm Im}\, J = \ker D$ and $R = \dim \ker D$.
  Assume there exists $x_0 \in K^n$ such that $D x_0 = e$, and let
  $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
  Let $y \in K^R$ denote the unique element of $K^n$ such that
  $x = x_0 + J y$. Then:
  \begin{enumerate}
  \item\label{reducD_item1}
    $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,{\bf 0},0)$.
  \item\label{reducD_item2}
    $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,{\bf 0},0)$ and
    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$\footnote{\simone{Est-ce que
    c'est bien $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$ ou plutôt la condition
    plus faible $\val \langle c,x^* \rangle = \val \langle J^T c,y^* \rangle$ ?
  Même question pour \Cref{solsLP}.}}.
  \end{enumerate}
\end{lemma}
\begin{proof}
  %The existence and uniqueness of $y$ are granted by the fact that $x \in x_0 + \ker D =x_0+ {\rm Im } J$  and $\ker J = \{0\}$. 
  First, if $D={\bf 0}$, then by the assumptions one must have $e=0$, and the problem
  is already reduced (with $J=I_n$ and $x_0=0$).
  Next, assume $D\neq{\bf 0}$, then $Dx=e$ and $Ax + b \le 0$ if and only if
  $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}. Finally, for all
  $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
\end{proof}

@@

\begin{lemma} \label{solsLP}
  Let $A \in K^{d\times n}$, $b \in K^d$, $c\in K^n$ and let
  $S = \mathrm{SNF}(A) = QAP^{-1} \in K^{d\times n}$, with
  $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$.
  Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
  Then
   \begin{enumerate}
   \item \label{solsLP_item1}
     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,{\bf 0},0)$ if and only if $y = P x \in K^n$ is
     feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
   \item \label{solsLP_item2}
     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,{\bf 0},0)$ if and only if $y^* = P x^*$ is
     a solution to \eqref{LP} with data $(S,b',c',{\bf 0},0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
   \end{enumerate}
\end{lemma}
\begin{proof}
  Note that the transition matrices $P$ and $Q$ defining SNF$(A)$ are invertible in $\OK$
  and as such they preserve inequalities: $Mz \geq 0$ if and only if $Nz \geq 0$, with
  $N = \mathrm{SNF}(M)$. Thus one has that $Ax+b = AP^{-1}y +b \geq 0$ if and only if
  $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
  Moreover, for all $c \in K^n$, we have $\langle c, x\rangle = \langle c, P^{-1}Px \rangle =
  \langle (P^{-1})^T c, Px \rangle = \langle c',y\rangle$, which proves
  \Cref{solsLP_item2}.
\end{proof}

@@

\begin{lemma}\label{prop:reduc}
  Let $(S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
  Then:
  \begin{enumerate}
  \item \label{prop:reduc_it1}
    \eqref{LP} with data $(S,b',c',{\bf 0},0)$ is feasible if and only if the $d-r$ last coefficients
    of $b'$ have nonnegative valuation, for $r = {\rm rank}\,S$.
  \item \label{prop:reduc_it2}
    Assume at least one of the $n-r$ last coefficients of $c'$ is non-zero. If \eqref{LP} with
    data $(S,b',c')$ is feasible, then it is unbounded and does not admit solutions.
  \end{enumerate}
\end{lemma}
\begin{proof}
  %%%%\corentin{préciser les notations}. 
  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
  $(S,b',c',0)$ if and only if $\val(s_i y_i + b'_i) \geq 0$ for\footnote{\simone{J'ai mis
    $\val(s_i y_i + b'_i) \geq 0$ au lieu de $\val(s_i y_i + b_i) \geq 0$ car c'est $b'$
    et non pas $b$.}} all $i = 1,\ldots,n$.
  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
  necessarily the $d-r$ last coefficients of $b'$ have nonnegative valuation.
  Conversely, if the $d-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
  $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
  with data $(S,b',c',{\bf 0},0)$.

  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$,
  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
  In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$. Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}. 
\end{proof}
